Project Description -- Erosion, Transport, Anomalous Diffusion, and Collapse in Granular and Porous Media

### 2019-11-16 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

>>>>

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.99 \textwidth]{./figs/collage.pdf}
\caption{\label{fig1} Geophysical examples of chemical and mechanical erosion. Top from left: Diagram of a coupled karst-soil system with conduit formation \cite{watson2019sinkholes}; Limestone pavement in Dent de Crolles, France; Nohoch Ch’en Sinkhole in Belize. Bottom: examples of soil erosion. The bottom right shows the microscopic soil texture.}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
